Layered Types -- A structured approach to arbitrarily combine Type Systems

### 2023-01-30 paper/use-cases.tex
* Removed unused sample tex files * Slight adaptions to first use case file

With these three layers, we have defined the complete type system for this use-case. Using these three layers we can now ensure the following properties of our program statically:

@@

>>>>

The final program with all layer annotations can be found in Listing \ref{lst:uc1_annotated}. With these three layers, we have defined the complete type system for this use-case. Using these three layers we can now ensure the following properties of our program statically:

@@

\begin{lstlisting}
-- Type Layer Definitions for externally defined functions
getLine :: types :: [string] -> int -> string
strToInt :: types :: string -> int
len :: types :: [string] -> int
createFD :: types :: string -> FileHandle
openFile :: types :: FileHandle -> void
readLines :: types :: FileHandle -> [string]
closeFile :: types :: FileHandle -> void
print :: types :: Any -> void

-- Layer definitions for type checking
logicalTypes :: typecheck :: bool
numTypes :: typecheck :: int
subtype :: typecheck :: int <: Any
subtype :: typecheck :: string <: Any

-- State layer definitions
createFD :: state :: {} -> { Closed }
openFile :: state :: {Closed => Open} -> {}
readLines :: state :: {Open => Consumed} -> {}
closeFile :: state :: {Consumed => Closed} -> {}

processLine :: types :: [string] -> int -> int -> int
processLine lines idx length {

    end :: types :: bool
    end := idx == length

        curLine :: types :: string
        curLine := getLine(lines, idx)

        number :: types :: int
        number := strToInt(curLine)

        greaterThanZero :: types :: bool
        greaterThanZero := number > 0

processLines :: types :: [string] -> int
processLines lines {
    length :: types :: int
    length := len(lines)

    idx :: types :: int
    idx := 0
    processLine(lines, idx, length)
}

fileName :: types :: string
fileName := "numbers.data"

fileDescriptor :: types :: FileHandle
fileDescriptor := createFD(fileName)

openFile(fileDescriptor)

lines :: types :: [string]
lines := readLines(fileDescriptor)

closeFile(fileDescriptor)

total :: types :: int
total := processLines(lines)

-- State post-conditions
-- The file handle is closed after the program has finished
fileDescriptor :: state :: {Closed}
\end{lstlisting}
